Democracy, Public Support, and Measurement Uncertainty

### 2021-05-18 paper/dcpo_demsupport.Rmd
adding moc into the manuscript

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools, mitools,
  boot, plm, # analysis
  flextable, 
  broomExtra, kableExtra, modelsummary, # tabulation
  gridExtra,
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse, janitor, glue, # data wrangling
  drhutools,
  dotwhisker # visualization
)

@@

source("../R/tidy_pgmm.r")

@@

claassen_replication <- readRDS("../data/claassen_replication.rds") %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)

load(here::here("data", "claassen_m5_theta.rda"))
load(here::here("data", "dcpo_input.rda"))
load(here::here("data", "dcpo_theta.rda"))
load(here::here("data", "dcpo_sigma.rda"))
load(here::here("data", "dem_mood_apsr.RData"))

@@

@@

\end{landscape}

>>>>

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools, mitools,
  boot, plm, # analysis
  flextable, 
  broomExtra, kableExtra, modelsummary, # tabulation
  gridExtra,
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse, janitor, glue, # data wrangling
  drhutools,
  dotwhisker, # visualization
  qs
)

@@

source(here::here("R", "tidy_pgmm.r"))
source(here::here("R", "moc_function.R"))

@@

claassen_replication <- readRDS("../data/claassen_replication.rds") %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)
load(here::here("data", "claassen_m5_theta.rda"))
load(here::here("data", "dem_mood_apsr.RData"))
# load(here::here("data", "dcpo_input.rda"))
# load(here::here("data", "dcpo_theta.rda"))
# load(here::here("data", "dcpo_sigma.rda"))

@@

dcpo_apsr_cntrl <- readRDS("data/cntrl_apsr_uncertainty.rds")
dcpo_apsr_analysis <- left_join(df_dcpo,dcpo_apsr_cntrl, by=c("country","year","iter"="iter_se") )
saveRDS(dcpo_apsr_analysis, "data/dcpo_analysis_apsr.rds")
qsave(dcpo_apsr_analysis, "data/dcpo_analysis_apsr_compress")

@@

\end{landscape}
# Replication with Alternative Methods Accounting for Uncertainty

```{r moc}
